---
title: "Seminar 5"
author: "\\newline Zhdankina Margarita, Kolesnikova Victoria, Romanov Sergey"
output: 
  pdf_document:
    latex_engine: xelatex
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
suppressPackageStartupMessages(library(coda))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(sna))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(igraph))
```


```{r include=FALSE}
all_net<-read.csv('AllNet.csv', header=TRUE, sep=";") # read data
rownames(all_net) <- all_net[,1]
all_net[,1] <- NULL
all_net<-as.matrix(all_net) # save it as a matrix
all_graph<-graph_from_adjacency_matrix(all_net) #create a graph


FriendMat<-read.csv("FriendNet.csv",header=TRUE, sep=";")
rownames(FriendMat) <- FriendMat[,1]
FriendMat[,1] <- NULL

ProfMat<-read.csv("ProfNet.csv",header=TRUE, sep=";")
rownames(ProfMat) <- ProfMat[,1]
ProfMat[,1] <- NULL

BossMat<-read.csv("BossNet.csv",header=TRUE, sep=";")
rownames(BossMat) <- BossMat[,1]
BossMat[,1] <- NULL


SupportMat<-read.csv("SupportNet.csv",header=TRUE, sep=";")
rownames(SupportMat) <- SupportMat[,1]
SupportMat[,1] <- NULL



FriendMat<-as.matrix(FriendMat)

ProfMat<-as.matrix(ProfMat)
BossMat<-as.matrix(BossMat)
SupportMat<-as.matrix(SupportMat)
Friend.any <- ifelse(FriendMat > 0, 1, 0)
Boss.any <- ifelse(BossMat > 0, 1, 0)
Prof.any <- ifelse(ProfMat > 0, 1, 0)
Support.any <- ifelse(SupportMat > 0, 1, 0)
```


```{r include=FALSE}
FriendGraph<-graph_from_adjacency_matrix(FriendMat,  weighted=TRUE)
ProfGraph<-graph_from_adjacency_matrix(ProfMat, weighted=TRUE)
BossGraph<-graph_from_adjacency_matrix(BossMat, weighted=TRUE)
SupportGraph<-graph_from_adjacency_matrix(SupportMat, weighted=TRUE)
FriendGraph.any <-graph.adjacency(Friend.any,
                                  mode=c("directed"),
                                  weighted=NULL,
                                  diag=FALSE)


BossGraph.any <-graph.adjacency(Boss.any,
                                mode=c("directed"),
                                weighted=NULL,
                                diag=FALSE)
ProfGraph.any <-graph.adjacency(Prof.any,
                                mode=c("directed"),
                                weighted=NULL,
                                diag=FALSE)



SupportGraph.any <-graph.adjacency(Support.any,
                                   mode=c("directed"),
                                   weighted=NULL,
                                   diag=FALSE)


ocb_att<-read.csv('ocb_att.csv', header=TRUE)
```

```{r include=FALSE}
age<-ocb_att$Age
sex<-ocb_att$Sex
#How long the person had this position: 
tenure<-ocb_att$WorkTitleYear+ocb_att$WorkTitleMonth/12
#How long worked in organization: 
tenure_org<-ocb_att$WorkOrgYear+ocb_att$WorkOrgMonth/12 
#How long reported to the same supervisor: 
tenure_sup<-ocb_att$RepSupYear+ocb_att$RepSupMonth/12
#Set of dummies for education:
ed1<-ifelse(ocb_att$Education==3,1,0) 
#this is for secondary specialized 
ed2<-ifelse(ocb_att$Education==4,1,0)
#this is higher
#Secondary, obviously, is the baseline
```

```{r include=FALSE}
#Physical participation variable
phys_part<-ocb_att$Phys_Part
```


# Assignment task 1

*Create a dummy set for work title*


```{r}
table(ocb_att$Title) # What work titles are included
```

```{r}
tit1<-ifelse(ocb_att$Title=='Assistant department head',1,0)
tit2<-ifelse(ocb_att$Title=='Department director',1,0)
tit3<-ifelse(ocb_att$Title=='Department head',1,0)
tit4<-ifelse(ocb_att$Title=='Head lawyer',1,0)
tit5<-ifelse(ocb_att$Title=='Lead specialist',1,0)
tit6<-ifelse(ocb_att$Title=='Project manager',1,0)
tit7<-ifelse(ocb_att$Title=='Specialist',1,0)
tit8<-ifelse(ocb_att$Title=='Subsidiary manager',1,0)
```

Lawyers are our baseline, because their sample is average


# Assignment task 2

*Test your dummy work title set in the regression above. Do you get anything worthwhile?*

```{r}
lm1<-lm(phys_part~tenure+tenure_sup + tit1+tit2+tit3+tit4+tit5+tit6+tit7+tit8)
summary(lm1)
```


As we can see, this model is significant (p-value = 0.004), but all set of dummies is not significant at all. R-square in comparison with the model without this set of dummies is bigger, but the significance tell us that this increase is nothing.

But maybe there can be a possibility that the 'level' of title can influence, not the exact title, so let's try another way of creating the dummies:

```{r}
lev1<-ifelse(ocb_att$Title=='Head lawyer',1,
             ifelse(ocb_att$Title=='Department director',1,
                    ifelse(ocb_att$Title=='Department head',1,
                           ifelse(ocb_att$Title=='Lead specialist',1,0))))


lev2<-ifelse(ocb_att$Title=='Lawyer',1,
             ifelse(ocb_att$Title=='Assistant department head',1,
                    ifelse(ocb_att$Title=='Project manager',1,
                           ifelse(ocb_att$Title=='pecialist',1,
                                  ifelse(ocb_att$Title=='Subsidiary manager',1,0)))))

```

Now let's try a model

```{r}
lm2<-lm(phys_part~tenure+tenure_sup + lev1)
summary(lm2)
```

As we can see, no changes - "level" of title is not significant, but let's try to use level-1 variable as a baseline 

```{r}
lm3<-lm(phys_part~tenure+tenure_sup + lev2)
summary(lm3)
```

Unfortunately, this did not help and the title still is not significant in this model.


```{r include=FALSE}
HR_att<-read.csv("OCB_att.csv",header=TRUE)
#Let's get the sex of our respondents into its own vector: 
sex<-HR_att$Sex
age<-HR_att$Age
#Dependent variables
Emotional_part<-HR_att$Emot_Part
Intent_to_leave<-HR_att$Intent_toLeave
Personal_conflicts<-HR_att$Personal_conflicts
#Predictors
#Challenge stressors:
Work_Quant<-HR_att$Work_quant #Work quantity 
Work_Resp<-HR_att$Work_Resp #Work responsibility 
Work_Diff<-HR_att$Work_Diff #work difficulty 
Work_Speed<-HR_att$Work_Speed # Work speed #Hindrance stressors: 
Work_Demands<-HR_att$Work_Demands
Admin_problems<-HR_att$Admin_problems
Personal_conflicts<-HR_att$Personal_conflicts
Org_Relations<-HR_att$Org_Relations
Role_Conflict<-HR_att$Role_Conflict
```

# Assignment task 3

*Try adding several other variables that could be theoretically appropriate. Can you find any that are significant in the model?*

Theoretically, almost all of the variables can be appropriate for influencing emotional participation, so for the first model we'll try to add organization relationships, intention to leave the job, demanding at work and role conflicts

```{r}
mod1<-lm(Emotional_part ~ Work_Resp + Work_Diff + Intent_to_leave
         + Org_Relations + Work_Demands + Role_Conflict)
summary(mod1)
```

This model is not so bad, it is significant and the R-squared = 0.51, which is quite high index for the model. And most of the predictors are significant, exept for intention to leave and work difficulty. So let's delete them from the model and try another time.

```{r}
mod2<-lm(Emotional_part ~ Work_Resp + Org_Relations + Work_Demands
         + Role_Conflict)
summary(mod2)
```

This model is good to, R-squared is still high = 0.51, but now role conflicts turned out insignificant, maybe that is because they can be correlated with the work difference, anyway, we'll exclude it too.


```{r}
mod3<-lm(Emotional_part ~ Work_Resp
         + Org_Relations + Work_Demands)
summary(mod3)
```

Finally, all of the predictors are significant, so we can say that this is our final model. Adjusted R-squared = 0.4958, which is a bit lower, but still good for the model. And the conclusions are that the amount responsibility and work demanding positively affect the emotional participation (when increasing by 1 point of predictor, it increases by 0.17337 and 0.37011 respectively), while organizational conflicts - negatively (when increasing by 1, emotional participation decreases by 0.27521)


```{r include=FALSE}
FriendMat<-read.csv("Friendnet.csv",header=TRUE)
ProfMat<-read.csv("Profnet.csv",header=TRUE)
BossMat<-read.csv("BossNet.csv",header=TRUE)
SupportMat<-read.csv("SupportNet.csv",header=TRUE)
FriendMat<-as.matrix(FriendMat)
ProfMat<-as.matrix(ProfMat)
BossMat<-as.matrix(BossMat)
SupportMat<-as.matrix(SupportMat)
```

```{r include=FALSE}
Friend.any <- ifelse(FriendMat > 0, 1, 0)
Boss.any <- ifelse(BossMat > 0, 1, 0)
Prof.any <- ifelse(ProfMat > 0, 1, 0)
Support.any <- ifelse(SupportMat > 0, 1, 0)
```



```{r include=FALSE}
indegree_Friend <- degree(FriendGraph.any, mode='in')
outdegree_Friend <- degree(FriendGraph.any, mode='out')
total_degree_Friend <- degree(FriendGraph.any, mode='total')
indegree_Support <- degree(SupportGraph.any, mode='in')
outdegree_Support <- degree(SupportGraph.any, mode='out')
total_degree_Support <- degree(SupportGraph.any, mode='total')
indegree_Prof <- degree(ProfGraph.any, mode='in')
outdegree_Prof <- degree(ProfGraph.any, mode='out')
total_degree_Prof <- degree(ProfGraph.any, mode='total')


#Betweenness and eigenvector: professional network?
betweenness_Prof <- betweenness(ProfGraph.any)
Prof_Evcent <- evcent(ProfGraph.any)
Prof_eigen <- Prof_Evcent$vector
```

# Assignment task 4

*Pass on other attributes to the graph. Select at least three and load them onto vertices.*


