---
title: "Seminar 7"
author: "\\newline Zhdankina Margarita, Kolesnikova Victoria, Romanov Sergey"
output: 
  pdf_document:
    latex_engine: xelatex
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
suppressPackageStartupMessages(library(coda))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(sna))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(igraph))
```


```{r eval=FALSE, include=FALSE}
SWFile <- "/SouthernWomen/SouthernWomen.tsv"
```

```{r eval=FALSE, include=FALSE}
SWFilePath <- paste(wd, SWFile, sep = "")
```

```{r eval=FALSE, include=FALSE}
SWrawdata<-read.table(SWFilePath, sep = "\t", header = TRUE, row.names = 1)
SWrawdata
```
# Assignment task 1

In your Seminar 7 folder, there is another file with data, HiTech. Create the code that will do the following:

- Create a directory that will consist of a working directory name and the HiTech folder name, so that it opens the HiTech folder.

- Create file paths to separate data files "GivesAdviceTo," "IsFriendOf," "ReportsTo," and "HiTechAtt.""

```{r}
wd<-getwd()
```


```{r}
HTFile1 <- "/HiTech/HiTech - GivesAdviceTo.tsv"
HTFilePath1 <- paste(wd, HTFile1, sep = "")
GivesAdviceTo<-read.table(HTFilePath1, sep = "\t", header = TRUE, row.names = 1)
head(GivesAdviceTo)

HTFile2 <- "/HiTech/HiTech - IsFriendOf.tsv"
HTFilePath2 <- paste(wd, HTFile2, sep = "")
IsFriendOf<-read.table(HTFilePath2, sep = "\t", header = TRUE, row.names = 1)
head(IsFriendOf)

HTFile3 <- "/HiTech/HiTech - ReportsTo.tsv"
HTFilePath3 <- paste(wd, HTFile3, sep = "")
ReportsTo<-read.table(HTFilePath3, sep = "\t", header = TRUE, row.names = 1)
head(ReportsTo)

HTFile4 <- "/HiTech/HiTech - HiTechAtt.tsv"
HTFilePath4 <- paste(wd, HTFile4, sep = "")
HiTechAtt<-read.table(HTFilePath4, sep = "\t", header = TRUE, row.names = 1)
head(HiTechAtt)
```

# Assignment task 2

Using the plotting function in igraph, improve my graph for the SouthernWomen data by changing at least three characteristics of the graph.

# Assignment task 3

Display the contents of the Women.only and Events.only matrices we created above.

- Explain what data in these matrices mean.

- What are the benefits and problems with separating incidence matrices and creating adjacency matrices out of them?

# Assignment task 4

For the network SouthernWomen, please calculate the following network characteristics and briefly explain what they mean:

- Indegree, outdegree, total degree;

- Centrality: degree, betweenness, closeness, eigenvector, page rank; correlations between these measures. 

- Transitivity.