---
title: "Seminar 7"
author: "\\newline Zhdankina Margarita, Kolesnikova Victoria, Romanov Sergey"
output: 
  pdf_document:
    latex_engine: xelatex
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
suppressPackageStartupMessages(library(coda))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(sna))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(igraph))
```


```{r eval=FALSE, include=FALSE}
SWFile <- "/SouthernWomen/SouthernWomen.tsv"
```

```{r eval=FALSE, include=FALSE}
SWFilePath <- paste(wd, SWFile, sep = "")
```

```{r eval=FALSE, include=FALSE}
SWrawdata<-read.table(SWFilePath, sep = "\t", header = TRUE, row.names = 1)
SWrawdata
```
# Assignment task 1

In your Seminar 7 folder, there is another file with data, HiTech. Create the code that will do the following:

- Create a directory that will consist of a working directory name and the HiTech folder name, so that it opens the HiTech folder.

- Create file paths to separate data files "GivesAdviceTo," "IsFriendOf," "ReportsTo," and "HiTechAtt.""

```{r}
wd<-getwd()
```


```{r}
HTFile1 <- "/HiTech/HiTech - GivesAdviceTo.tsv"
HTFilePath1 <- paste(wd, HTFile1, sep = "")
GivesAdviceTo<-read.table(HTFilePath1, sep = "\t", header = TRUE, row.names = 1)
head(GivesAdviceTo)

HTFile2 <- "/HiTech/HiTech - IsFriendOf.tsv"
HTFilePath2 <- paste(wd, HTFile2, sep = "")
IsFriendOf<-read.table(HTFilePath2, sep = "\t", header = TRUE, row.names = 1)
head(IsFriendOf)

HTFile3 <- "/HiTech/HiTech - ReportsTo.tsv"
HTFilePath3 <- paste(wd, HTFile3, sep = "")
ReportsTo<-read.table(HTFilePath3, sep = "\t", header = TRUE, row.names = 1)
head(ReportsTo)

HTFile4 <- "/HiTech/HiTech - HiTechAtt.tsv"
HTFilePath4 <- paste(wd, HTFile4, sep = "")
HiTechAtt<-read.table(HTFilePath4, sep = "\t", header = TRUE, row.names = 1)
head(HiTechAtt)
```

# Assignment task 2

Using the plotting function in igraph, improve my graph for the SouthernWomen data by changing at least three characteristics of the graph.

# Assignment task 3

Display the contents of the Women.only and Events.only matrices we created above.

- Explain what data in these matrices mean.

- What are the benefits and problems with separating incidence matrices and creating adjacency matrices out of them?

# Assignment task 4

For the network SouthernWomen, please calculate the following network characteristics and briefly explain what they mean:

- Indegree, outdegree, total degree;

- Centrality: degree, betweenness, closeness, eigenvector, page rank; correlations between these measures. 

- Transitivity.


```{r}
degree <- data.frame(row.names = V(SWnet.sep$proj1)$name,
                    T_degree = degree(SWnet.sep$proj1, mode ="total"),
                    O_degree = degree(SWnet.sep$proj1, mode= "out"), 
                    I_degree = degree(SWnet.sep$proj1, mode= "in"))
                         
                         
kable(degree, row.names=T, label="Degrees")                         
```
As our network is made undirected all types of degree are equal to each other. Theresa is has the biggest degree centralites. 

```{r}
centralities <- data.frame(row.names = V(SWnet.sep$proj1)$name,
                         degree = degree(SWnet.sep$proj1),
                         betweenness = betweenness(SWnet.sep$proj1),
                         closeness =  closeness(SWnet.sep$proj1),
                         eigenvector = evcent(SWnet.sep$proj1)$vector,
                         page_rank = page_rank(SWnet.sep$proj1)$vector)
                         
                         
kable(centralities, row.names=T, label="Southern Women Centrality")                         
```
While Olivia and Flora are the highest in betweenness and closeness centralities, Therersa is leading in eigen and page rank figures.With regard to the least numbers, the belong to the same nodes but vise versa: Theresa is smallest in  betweenness and closeness, and Olivia and Flora are in eigen and page rank.

```{r}
cor(centralities)                       
```
Because degree, page_rank and eigen vector are computed without pathways they negatively correlate with betweenness and
closeness centrality. 

```{r}
transitivity(SWnet.sep$proj1)
```
As we can see, Southern Women Network is almost fully transitive. 
