---
title: "Seminar 3"
author: "\\newline Zhdankina Margarita, Kolesnikova Victoria, Romanov Sergey"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library('sna')
library('network')
load('flo.Rdata')
```

# Assignment question 1

*Given the information we’ve discussed about triads, what conclusions can you make about the results of the triadic census analysis for the Florentine Family network?*

First of all, the largest number of triads are null, that is, no one is in contact with anyone, there are only 3 mutual triads. 

Secondly, Florentine Families have only 1 type of biological triads - 102, all other biological triads are not presented in this network, which can be due to the specific structure of  social communication model of that time, because triads like 012 or 021D look quite strange in context of families and their communications.

Third, 201 triad type is presented 38 times, which can be due to the presence of "bridges" between different families.

Thus, Florentine Families are not so connected by triads and there are many structural holes in this network, may be with the presence of little number of small clusters (3 mutual triads and 31 201 triads may indicate that).

# Assignment question 2 

*Given the explanation of transitivity provided, how do you evaluate the transitivity coefficient obtained with the above command?*

```{r echo=TRUE}
gtrans(flo.marriage, measure='weak')
```

Let us create one random directed graph with the same amount of nodes

```{r echo=TRUE}
num_nodes <- 16
my_matrix<-matrix(round(runif(num_nodes*num_nodes)), ncol = num_nodes)
diag(my_matrix) <- 0
my_network<-as.network(x = my_matrix, directed = TRUE )
gtrans(my_network, measure='weak')
```


The observed figure of transitivity is less than random figures. Thus, in Medici'stimes, families tend to form less ties than possible. It gives us a hint that something restricts them from creating possible connections.

# Assignment question 3

*Here, we showed you how to calculate this measure and its different types, but the information you get will be meaningless. Why?*

```{r echo=TRUE}
grecip(flo.marriage, measure = 'dyadic') # why not 0?
grecip(flo.marriage, measure = 'dyadic.nonnull')
grecip(flo.marriage, measure = 'edgewise')
grecip(flo.marriage, measure = 'edgewise.lrr')
grecip(flo.marriage, measure = 'correlation')
```

In that case, those commands are meaningless, because ties represent marriage and business relations which are reciprocal by definition.

# Assignment question 4

*What can you say about the last two commands? Why is the result what it is?*

In this case there is no difference between this 2 commands because the Florentine Families network is undirected, so there is no difference how to calculate - path *to* node or *from* node, the result will be the same.


# Assignment task 5

*Examine various ways to calculate distances in a graph. Calculate one measure not shown above for our Florentine Families network. Remember to use the graph object!*

```{r echo=TRUE, warning=FALSE}
detach(package:sna)
detach(package:network)
library(igraph)
suppressPackageStartupMessages(library(intergraph))
flo.graph<-asIgraph(flo.marriage)
class(flo.graph)
```

here is another method in measuring distances 

```{r echo=TRUE}
shortest_paths(flo.graph, 1, to = V(flo.graph))
```

# Seminar assignment 6

## 6.1

*Take a careful look at the table with Florentine family centralities. Can you figure out why the name "Medici" is familiar to us, and others - not so much? Which centrality, in your opinion, is the most "responsible"" for this?*

The most "responsible" centralities are Alpha and Bonacich centrality, cause based on eigenvector centralities they should be as high as possible, but here we can see that there is some problem with it. Ridolfi has the greatest Alpha centrality and Albizzi has the greatest Bonacich centrality. Medici has an average index of centrality in this case, so based on them we can say that Madici is familiar to us, and others - not so much.

## 6.2

*Interpret correlation matrix of the Florentine family centralities. What do you conclude?*

Firstly, in and out degrees have coeff = 1.0 for the same reason as in the assignment no. 3: The network is symmetric. As for the correlation between degrees and other measures of centrality, it is always above 0.75, which seems logical, asthe amount of in and out edges, one way or another, is involved in the computations of betweenness, closeness, and eigen-centrality. In the third term, the correlation between closeness and betweenness is the smallest one (0.567) among all. Provided that betweenness represents brokerage and control over information, it is clear that closeness, which has relatively opposite meaning, correlates less with betweenness than with others: The better information spreads(closeness), the less the possibility of structural holes, which provides the information control (betweenness). The same reason explains why eigen-vector correlates(0.67) with betweenness less than with degrees(0.94) or closeness(0.79). Eigen centrality is more related to the social capital and connected more to the valuable nodes than to the structural holes.While eigen and closeness figures depend on the same things as betweeness - the amount of ties, betweeness depends also on structural holes. Finally, as we can see, eigen-vector centrality correlates with closeness for the already mentioned reasons.

## 6.3

*From the long list of possible centralities, pick any five, plus Bonacich, Page Rank, and Katz, to analyze for Florentine families.*
